### 2015-03-15 README.Rmd
modified readme file

# qmj (Quality Minus Junk)
Authors : Ryan Kwon, Anthoney Tsou

@@

```{r}
#Now let's look at a graph for quality.
data(quality)
second_qmj <- qmjs[[2]]
```
```{r fig.width=7, fig.height=6}
library(ggplot2)
plot_quality(second_qmj, quality)
```

>>>>

# qmj (Quality Minus Junk)
Authors : Anthoney Tsou, David Kane, Ryan Kwon

@@

```{r}
#Now let's look at a graph for quality.
data(quality)
second_qmj <- qmjs[[2]]
```
```{r fig.width=7, fig.height=6}
plot_quality(second_qmj, quality)
```
